% Statistical learning procedures. Refitting the model of interest on each sample set.

The previously described dataset is partitioned into different subsets
to apply some statistical methods that usually
improves the robustness of the experiments
when performing machine learning tasks.
At a higher level,
the data is divided into two groups: the $development$ set and the \textit{hold-out} or $validation$ set. The former is used to fit the different models while the latter is used
to evaluate the performance
of the final model on unseen data. At the same time, the $development$ set is divided in four
subsets in order to apply \textit{k-fold cross validation} ($k=4$), a
technique that leads to more accurate estimates of the errors when exploring different
models in the training phase.

\subsection{Hold-Out Set}

The \textit{hold-out} set or \textit{validation} set is a subset of the data that is kept
separately of the training set and remains untouched until the final model is fitted. It is
then used to test the final model and verify if it generalizes to unseen data.
Additionally, it allows
an unbiased estimate for the test error because none of the instances was used in the
fitting process. It is worth nothing that in order to keep this condition true, the samples
of the hold-out set must come speakers that are not used in the training set.

The partitioning is carried out at speaker level. Speakers are randomly split into two groups
that contain 20\% and 80\% of the total number of speakers. The hold-out set
is obtained from the group with 20\% of the speakers by gathering all the utterances pronounced
by those speakers. The training set is obtained from the
group with 80\% of the speakers in the same way.
