In this section we describe some relevant parameters that are computed before training the
models.

The first parameter to be described is the number of mixtures components
to be computed when training the GMM for each phone. As it is described in Method Section
\ref{subsection:gmm}, in order to extract the supervectors an initial GMM-UBM is trained
using all the instances of a given phone.
The number of Gaussian Mixtures to be trained is kept proportional to the number of
training instances for that phone. In the current work, a
mixture component is trained every 15 phone instances
in order to keep a similar proportion to what was used in the previous work \cite{main} .

Regarding to the SVM classifiers, two relevant parameters are tunned. The first one is
the default value of the $C$ parameter, which is described in Section
\ref{subsection:soft_margin}.
Different values of the \textcolor{red}{input parameter $C$ (which is set to 1.0 by default
in \textit{sklearn})}
were tested at the beginning of the
current work using at first an exponential scale:
$10^{-i} \ldots 10^{i}$ with $i=4$, an after that reducing the search interval to
$[0 \ldots 1]$. The best results, however, were obtained when using a default value
suggested in the docs of SVM-Light, an implementation of SVMs in C language: $\frac{1}{avg(x*x)}$,
\textcolor{red}{that is the average of the squared norm of the instances}.

Finally, another important parameter is described with regard to the SVM classifier.
A \textit{class-weight} parameter is provided by \textit{sklearn}, which allows to
adjust the weight of the $C$ parameter for each class. If not given, all classes are supposed
to weight one. In the curent work, this parameter is set to ``balanced'', which adjusts
the weights inversely proportional to the class frequencies in the input data.
This is particular useful in our case, because the number of instances for each class is
unbalanced for most of the phones.


